---
title: "Script for all calculations - SDG Interactions Nepal"
author: "Biraj Adhikari"
date: "2023-04-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r requirements1}
library(readxl)
library(dplyr)
library(ggrepel) #for geom_text_repel
library(ggplot2)
library(ggpubr)
library(tidyr)

fct_case_when <- function(...) {
  args <- as.list(match.call())
  levels <- sapply(args[-1], function(f) f[[3]])  # extract RHS of formula
  levels <- levels[!is.na(levels)]
  factor(dplyr::case_when(...), levels=levels)
}
```

# Method 1: Seven-Point Likert Scale:  
## Fig. 2
```{r reading and formatting data: method 1}
maindat = read_xlsx('Alldata.xlsx', sheet = "method1")

#Assigning appropriate labels:
maindat = maindat %>%
  
    mutate(sdgout_def = fct_case_when(
    sdgout == "sdg17.14" ~ "SDG 17.14: Policy Coherence",
    sdgout == "sdg16.5" ~ "SDG 16.5: Reduced Corruption",
    sdgout == "sdg16.3" ~ "SDG 16.3: Rule of Law",
    sdgout == "sdg13.3" ~ "SDG 13.3: Climate Change Capacity",
    sdgout == "sdg13.2" ~ "SDG 13.2: Climate Change Measures",
    sdgout == "sdg13.1" ~ "SDG 13.1: Climate Change Resilience",
    sdgout == "sdg12.2" ~ "SDG 12.2: Natural Resource Management",
    sdgout == "sdg11.4" ~ "SDG 11.4: Heritage",
    sdgout == "sdg11.3" ~ "SDG 11.3: Urbanization",
    sdgout == "sdg10.2" ~ "SDG 10.2: Inclusivity",
    sdgout == "sdg10.1" ~ "SDG 10.1: Reduced Inequalities",
    sdgout == "sdg9.2" ~ "SDG 9.2: Industrialization",
    sdgout == "sdg9.1" ~ "SDG 9.1: Infrastructure",
    sdgout == "sdg8.9" ~ "SDG 8.9: Sustainable Tourism",
    sdgout == "sdg8.1" ~ "SDG 8.1: Economic Growth",
    sdgout == "sdg7.2" ~ "SDG 7.2: Renewable Energy",
    sdgout == "sdg7.1" ~ "SDG 7.1: Universal Energy Access",
    sdgout == "sdg6.3" ~ "SDG 6.3: Water Quality",
    sdgout == "sdg6.1" ~ "SDG 6.1: Water Access",
    sdgout == "sdg5.5" ~ "SDG 5.5: Gender Inclusivity",
    sdgout == "sdg5.1" ~ "SDG 5.1: No Gender Discrimination",
    sdgout == "sdg4.7" ~ "SDG 4.7: Sustainability Education",
    sdgout == "sdg4.3" ~ "SDG 4.3: Education Access",
    sdgout == "sdg3.8" ~ "SDG 3.8: Universal Health Access",
    sdgout == "sdg3.4" ~ "SDG 3.4: Reduced Mortality",
    sdgout == "sdg2.4" ~ "SDG 2.4: Food Sustainability",
    sdgout == "sdg2.3" ~ "SDG 2.3: Food Productivity",
    sdgout == "sdg2.1" ~ "SDG 2.1: Universal Food Access",
    sdgout == "sdg1.3" ~ "SDG 1.3: Social Protection",
    sdgout == "sdg1.2" ~ "SDG 1.2: Poverty Reduction"
  )) %>%
  
  mutate(sdgout = fct_case_when(
    sdgout == "sdg17.14" ~ "SDG 17.14",
    sdgout == "sdg16.5" ~ "SDG 16.5",
    sdgout == "sdg16.3" ~ "SDG 16.3",
    sdgout == "sdg13.3" ~ "SDG 13.3",
    sdgout == "sdg13.2" ~ "SDG 13.2",
    sdgout == "sdg13.1" ~ "SDG 31.1",
    sdgout == "sdg12.2" ~ "SDG 12.2",
    sdgout == "sdg11.4" ~ "SDG 11.4",
    sdgout == "sdg11.3" ~ "SDG 11.3",
    sdgout == "sdg10.2" ~ "SDG 10.2",
    sdgout == "sdg10.1" ~ "SDG 10.1",
    sdgout == "sdg9.2" ~ "SDG 9.2",
    sdgout == "sdg9.1" ~ "SDG 9.1",
    sdgout == "sdg8.9" ~ "SDG 8.9",
    sdgout == "sdg8.1" ~ "SDG 8.1",
    sdgout == "sdg7.2" ~ "SDG 7.2",
    sdgout == "sdg7.1" ~ "SDG 7.1",
    sdgout == "sdg6.3" ~ "SDG 6.3",
    sdgout == "sdg6.1" ~ "SDG 6.1",
    sdgout == "sdg5.5" ~ "SDG 5.5",
    sdgout == "sdg5.1" ~ "SDG 5.1",
    sdgout == "sdg4.7" ~ "SDG 4.7",
    sdgout == "sdg4.3" ~ "SDG 4.3",
    sdgout == "sdg3.8" ~ "SDG 3.8",
    sdgout == "sdg3.4" ~ "SDG 3.4",
    sdgout == "sdg2.4" ~ "SDG 2.4",
    sdgout == "sdg2.3" ~ "SDG 2.3",
    sdgout == "sdg2.1" ~ "SDG 2.1",
    sdgout == "sdg1.3" ~ "SDG 1.3",
    sdgout == "sdg1.2" ~ "SDG 1.2"
  )) %>%
  
    mutate(sdgin = fct_case_when(
    sdgin == "sdg17.14" ~ "SDG 17.14",
    sdgin == "sdg16.5" ~ "SDG 16.5",
    sdgin == "sdg16.3" ~ "SDG 16.3",
    sdgin == "sdg13.3" ~ "SDG 13.3",
    sdgin == "sdg13.2" ~ "SDG 13.2",
    sdgin == "sdg13.1" ~ "SDG 31.1",
    sdgin == "sdg12.2" ~ "SDG 12.2",
    sdgin == "sdg11.4" ~ "SDG 11.4",
    sdgin == "sdg11.3" ~ "SDG 11.3",
    sdgin == "sdg10.2" ~ "SDG 10.2",
    sdgin == "sdg10.1" ~ "SDG 10.1",
    sdgin == "sdg9.2" ~ "SDG 9.2",
    sdgin == "sdg9.1" ~ "SDG 9.1",
    sdgin == "sdg8.9" ~ "SDG 8.9",
    sdgin == "sdg8.1" ~ "SDG 8.1",
    sdgin == "sdg7.2" ~ "SDG 7.2",
    sdgin == "sdg7.1" ~ "SDG 7.1",
    sdgin == "sdg6.3" ~ "SDG 6.3",
    sdgin == "sdg6.1" ~ "SDG 6.1",
    sdgin == "sdg5.5" ~ "SDG 5.5",
    sdgin == "sdg5.1" ~ "SDG 5.1",
    sdgin == "sdg4.7" ~ "SDG 4.7",
    sdgin == "sdg4.3" ~ "SDG 4.3",
    sdgin == "sdg3.8" ~ "SDG 3.8",
    sdgin == "sdg3.4" ~ "SDG 3.4",
    sdgin == "sdg2.4" ~ "SDG 2.4",
    sdgin == "sdg2.3" ~ "SDG 2.3",
    sdgin == "sdg2.1" ~ "SDG 2.1",
    sdgin == "sdg1.3" ~ "SDG 1.3",
    sdgin == "sdg1.2" ~ "SDG 1.2"
  ))
```

### Outgoing Interactions
```{r preparing plot}
#making outscore a categorical variable for visualization purposes
outsc_cat = maindat
outsc_cat$outscore = factor(outsc_cat$outscore, levels = c("-3", "-2", "-1", "0", "1", "2", "3"))

#calculating the frequency of various outscores per sdg and calculating percentage of each outscore per sdg
for_outsc_vis = outsc_cat %>% group_by(sdgout_def, outscore) %>% dplyr::summarise(n = n())
for_outsc_vis = for_outsc_vis %>% group_by(sdgout_def) %>% mutate(pc = round(n/sum(n),2))

#to make divergent stacked bar plot
for_outsc_vis = for_outsc_vis %>% mutate(pc = if_else(outscore == "0", pc/2, pc))

#to add labels left and right of the fig
poslabel = for_outsc_vis %>% filter(outscore %in% c("1", "2", "3")) %>% group_by(sdgout_def) %>% dplyr::summarize(poslab = sum(pc))
neglabel = for_outsc_vis %>% filter(outscore %in% c("-1", "-2", "-3")) %>% group_by(sdgout_def) %>% dplyr::summarize(neglab = sum(pc))

#making the ggplot
outscore_fig = ggplot() +

  #making the positive values first
  geom_col(data = filter(for_outsc_vis, outscore %in% c("0", "1", "2", "3")), 
           aes(x = sdgout_def, y = pc, fill = outscore),
           position = position_stack(reverse = T)) +
  
#these are the negative values
  geom_col(data = filter(for_outsc_vis, outscore %in% c("0", "-1", "-2", "-3")),
           aes(x = sdgout_def, y = -pc, fill = outscore), position = position_stack()) +
  
#adding neutral value percentage labels (in the middle)  
  geom_text(data = filter(for_outsc_vis, outscore == "0"), aes(x = sdgout_def, y = 0, label = paste(pc*2*100, "%")), size = 4) +
  
#adding positive labels (in the right)
  geom_text(data = poslabel, aes(x = sdgout_def, y = 1.15, label = paste(poslab*100,"%")), size =4, color = "#1572d1") + 
  
#adding negative labels (in the left)
  geom_text(data = neglabel, aes(x = sdgout_def, y = -0.65, label = paste(neglab*100, "%")), size =4, color = "#e6470e") + 
  
  scale_fill_brewer(palette = "RdBu", drop = FALSE,
                    labels = c("(-3) Canceling", "(-2) Counteracting",  "(-1) Constraining", "(0) Consistent", "(+1) Enabling", "(+2) Reinforcing", "(+3) Indivisible")) +
  
  theme_minimal() +
  labs(title = "(a) Outgoing Interactions towards SDG 15")+
  xlab("SDG Targets") +
     
    theme(
        plot.title = element_text(hjust = 0.5, size = 15),
        legend.title = element_blank(),
        legend.text = element_text(size = 15),
        axis.text.x = element_blank(),
        axis.title.y = element_text(size = 15),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 12)
        ) +

  coord_flip()

outscore_fig

rm(list = c('poslabel','neglabel','outsc_cat'))

```

### Incoming Interactions
```{r}
#making inscore a categorical variable for visualization purposes
insc_cat = maindat
insc_cat$inscore = factor(insc_cat$inscore, levels = c("-3", "-2", "-1", "0", "1", "2", "3"))

#calculating the frequency of various inscores per sdg and calculating percentage of each inscore per sdg
for_insc_vis = insc_cat %>% group_by(sdgin, inscore) %>% summarise(n = n())
for_insc_vis = for_insc_vis %>% group_by(sdgin) %>% mutate(pc = round(n/sum(n),2))

#to make divergent stacked bar plot
for_insc_vis %>% mutate(pc = if_else(inscore == "0", pc/2, pc))

#to add labels left and right of the fig
poslabel = for_insc_vis %>% filter(inscore %in% c("1", "2", "3")) %>% group_by(sdgin) %>% summarize(poslab = sum(pc))
neglabel = for_insc_vis %>% filter(inscore %in% c("-1", "-2", "-3")) %>% group_by(sdgin) %>% summarize(neglab = sum(pc))

#making the ggplot
inscore_fig = ggplot() +

  #making the positive values first
  geom_col(data = filter(for_insc_vis, inscore %in% c("0", "1", "2", "3")), 
           aes(x = sdgin, y = pc, fill = inscore),
           position = position_stack(reverse = T)) +
  
#these are the negative values
  geom_col(data = filter(for_insc_vis, inscore %in% c("0", "-1", "-2", "-3")),
           aes(x = sdgin, y = -pc, fill = inscore), position = position_stack()) +
  
#adding neutral value percentage labels (in the middle)  
  geom_text(data = filter(for_insc_vis, inscore == "0"), aes(x = sdgin, y = 0, label = paste(pc*2*100, "%")), size = 4) +
  
#adding positive labels (in the right)
  geom_text(data = poslabel, aes(x = sdgin, y = 1.15, label = paste(poslab*100,"%")), size =4, color = "#1572d1") + 
  
#adding negative labels (in the left)
  geom_text(data = neglabel, aes(x = sdgin, y = -0.65, label = paste(neglab*100, "%")), size =4, color = "#e6470e") + 

scale_fill_brewer(palette = "RdBu", drop = FALSE,
     labels = c("(-3) Canceling", "(-2) Counteracting",  "(-1) Constraining", "(0)     Consistent", "(+1)       Enabling", "(+2) Reinforcing", "(+3) Indivisible")) +
  
scale_x_discrete(position = "top") + 
  
  theme_minimal() +
 labs(title = "(b) Incoming Interactions from SDG 15", x = "") + 
  theme(
      plot.title = element_text(hjust = 0.5, size = 15),
        legend.title = element_blank(),
        legend.text = element_text(size = 15),
      axis.text.x = element_blank(),
      axis.title.x = element_blank(),
      axis.text.y = element_text(size = 12)
        ) +

  coord_flip()

inscore_fig
```

### Combining Outgoing and Incoming Interactions
```{r}
png(filename = "Figure2.png",            
  width = 3800,        
  height = 3000,
  res = 300,  
  ) 

ggarrange(outscore_fig, NULL, inscore_fig + rremove("y.text"), widths = c(1.7,0.1, 1), nrow = 1, ncol = 3, common.legend = TRUE, legend = "bottom")

rm(for_insc_vis, for_outsc_vis, insc_cat, inscore_fig, 
            maindat, neglabel, outscore_fig, poslabel)
```

## Fig. 3
```{r reading data - fig 3}
maindat = read_xlsx('Alldata.xlsx', sheet = "method1")
maindat = maindat %>% select(-sdgin) %>% rename(SDGs = sdgout)

maindat$SDGs = factor(maindat$SDGs, levels = c("sdg1.2", "sdg1.3", "sdg2.1", "sdg2.3", "sdg2.4", "sdg3.4", "sdg3.8", "sdg4.3", "sdg4.7", "sdg5.1", "sdg5.5", "sdg6.1", "sdg6.3", "sdg7.1", "sdg7.2", "sdg8.1", "sdg8.9", "sdg9.1", "sdg9.2", "sdg10.1", "sdg10.2", "sdg11.3", "sdg11.4", "sdg12.2", "sdg13.1", "sdg13.2", "sdg13.3", "sdg16.3", "sdg16.5", "sdg17.14"))
```

### Fig 3a (AR and IC for other goals)
```{r required calculations}
#STEP 1: for each SDGt target, we first calculate the median positive outgoing, median negative outgoing, median positive incoming and median negative incoming interactions::
#in cases where the median confidence of each score is >3 (ie uncertain), we have excluded it from our analysis

pos_out = maindat %>% filter(outscore>0) %>%
  group_by(SDGs) %>%
  summarize (
             med_pos_outscore = median(outscore),
             pos_outscore_med_conf = median(conf_out)
             ) %>%
  filter(pos_outscore_med_conf < 3)
             
neg_out = maindat %>% filter(outscore <0) %>%
group_by(SDGs) %>%
  summarize(
            med_neg_outscore = median(outscore),
            neg_outscore_med_conf = median(conf_out)
             ) %>%
  filter(neg_outscore_med_conf < 3)

pos_in = maindat %>% filter(inscore > 0) %>%
  group_by(SDGs) %>%
  summarize(
            med_pos_inscore = median(inscore),
            pos_inscore_med_conf = median(conf_in)
            ) %>%
  filter(pos_inscore_med_conf < 3)

neg_in = maindat %>% filter(inscore < 0) %>%
  group_by(SDGs) %>%
  summarize(
            med_neg_inscore = median(inscore),
            neg_inscore_med_conf = median(conf_in)
            ) %>%
  filter(neg_inscore_med_conf < 3)


#merging all of the calculated values above
sdgstat_all = merge(pos_out, neg_out, by = "SDGs", all = TRUE)
sdgstat_all = merge(sdgstat_all, pos_in, by = "SDGs", all =  TRUE)
sdgstat_all = merge(sdgstat_all, neg_in, by = "SDGs", all =  TRUE)



sdgstat_all = sdgstat_all %>% separate(SDGs, c("Goal", "Target"))

#STEP 2: Calculating Weigted Interaction scores for goal level. Note: the division by n() is so that the scores are not affected by the number of targets taken for each SDG (For example, SDG 12 has only one target and SDG 13 has 3 targets.)
sdgstat_all = sdgstat_all %>% group_by(Goal) %>% summarize(Weighted.Outscore.Pos = sum(med_pos_outscore, na.rm = TRUE)/n(),
                                                           Weighted.Outscore.Neg = sum(med_neg_outscore, na.rm = TRUE)/n(),
                                                           Weighted.Inscore.Pos = sum(med_pos_inscore, na.rm = TRUE)/n(),
                                                           Weighted.Inscore.Neg = sum(med_neg_inscore, na.rm = TRUE)/n())

sdgstat_all = sdgstat_all %>%
  mutate(Goal = fct_case_when(
     Goal == "sdg1" ~ "SDG 1",
     Goal == "sdg2" ~ "SDG 2",
     Goal == "sdg3" ~ "SDG 3",
     Goal == "sdg4" ~ "SDG 4",
     Goal == "sdg5" ~ "SDG 5",
     Goal == "sdg6" ~ "SDG 6",
     Goal == "sdg7" ~ "SDG 7",
     Goal == "sdg8" ~ "SDG 8",
     Goal == "sdg9" ~ "SDG 9",
     Goal == "sdg10" ~ "SDG 10",
     Goal == "sdg11" ~ "SDG 11",
     Goal == "sdg12" ~ "SDG 12",
     Goal == "sdg13" ~ "SDG 13",
     Goal == "sdg16" ~ "SDG 16",
     Goal == "sdg17" ~ "SDG 17"
  ))



#calculating ARs and ICs
sdgstat_all = sdgstat_all %>%
  mutate(AR_pos = Weighted.Outscore.Pos/Weighted.Inscore.Pos) %>%
  mutate(AR_neg = Weighted.Outscore.Neg/Weighted.Inscore.Neg) %>%
  mutate(IC_pos = Weighted.Outscore.Pos * Weighted.Inscore.Pos) %>%
  mutate(IC_neg = Weighted.Outscore.Neg * Weighted.Inscore.Neg)

rm(neg_in, neg_out, pos_in, pos_out)
```
  
Final Adjustments
```{r final adjustments - fig 3}
#removing NAs and Infs
df_posAR = sdgstat_all %>% select(Goal, AR_pos) %>% filter(!is.na(AR_pos)) %>% filter(!is.infinite(AR_pos)) %>% filter(AR_pos !=0)
df_negAR = sdgstat_all %>% select(Goal, AR_neg) %>% filter(!is.na(AR_neg)) %>% filter(!is.infinite(AR_neg)) %>% filter(AR_neg !=0)
df_posIC = sdgstat_all %>% select(Goal, IC_pos) %>% filter(!is.na(IC_pos)) %>% filter(!is.infinite(IC_pos)) %>% filter(IC_pos !=0)
df_negIC = sdgstat_all %>% select(Goal, IC_neg) %>% filter(!is.na(IC_neg)) %>% filter(!is.infinite(IC_neg)) %>% filter (IC_neg !=0)

forplot = merge(df_posAR, df_negAR, by = "Goal", all = TRUE)
forplot = merge(forplot, df_posIC, by = "Goal", all = TRUE)
forplot = merge(forplot, df_negIC, by = "Goal", all = TRUE)
colnames(forplot) = c("SDG", "AR_pos", "AR_neg", "IC_pos", "IC_neg")

rm(df_posAR, df_negAR, df_posIC, df_negIC)
```
  
  Making the figure:

```{r AR IC - Fig 3a}
#now we have all we need to plot
#plotting the data
png(filename = "Figure3a.png",
    width = 2000,
    height = 1500,
    res = 300)

bm_all = ggplot() +

  #positive AR/IC
    geom_point(data = forplot, aes(x = AR_pos, y = IC_pos), color = "#4393c3", shape = 16, size = 2.5) +
    geom_text_repel(data = forplot, aes(x = AR_pos, y = IC_pos, label = SDG),
            color = "#4393c3", size = 2.4, min.segment.length = Inf, box.padding = 0.1) +
  #negative AR/IC  
  geom_point(data = forplot, aes(x = AR_neg, y = IC_neg), color = "#d6604d", shape = 17, size = 2.5) +
  geom_text_repel(data = forplot, aes(x = AR_neg, y = IC_neg, label = SDG),
            color = "#d6604d", size = 2.4) +
  
  geom_vline(xintercept = 1) +
  scale_x_continuous(trans = "log10",
                     breaks = c(0.5, 0.8, 1, 2, 3)) +
  
  labs(x = "Activity Ratio", y = "Interconnectedness") + 
  annotate(geom = "text", x = 0.75, y = 3, label = "Buffers", 
           fontface = 'italic', size = 3.5) +
  annotate(geom = "text", x = 1.7, y = 3, label = "Multipliers", 
           fontface = 'italic', size = 3.5) +
  
  #some more explanation of labels

  annotate(geom = "text", x = 1, y = -1, label = "(Weak Influence)", 
           fontface = 'italic', size = 3) +

  annotate(geom = "text", x = 1, y = 8.8, label = "(Strong Influence)", 
           fontface = 'italic', size = 3) +
  
  coord_cartesian(ylim = c(0, 8), clip = "off") +
  labs(title = "(a)") +
  
  theme(axis.title = element_text(size = 10),
        axis.text = element_text(size = 7),
        panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(size = 0.45, linetype = "solid", colour = "#F0F0F0"),
        panel.grid.minor = element_line(size = 0.45, linetype = "solid", colour = "#F0F0F0"),
        plot.margin = unit(c(0.8,0,0.8,0), "cm"))
  

bm_all
dev.off()
```
  
### Fig 3b (AR and IC for SDG 15)
```{r}
pos_out = maindat %>% filter(inscore >0) %>% group_by(SDGs) %>% summarize(median_inscore_pos = median(inscore))
neg_out = maindat %>% filter(inscore <0) %>% group_by(SDGs) %>% summarize(median_inscore_neg = median(inscore))

outdegree_pos = sum(pos_out$median_inscore_pos)
outdegree_neg = sum(neg_out$median_inscore_neg)

pos_in = maindat %>% filter(outscore >0) %>% group_by(SDGs) %>% summarize(median_outscore_pos = median(outscore))
neg_in = maindat %>% filter(outscore <0) %>% group_by(SDGs) %>% summarize(median_outscore_neg = median(outscore))

indegree_pos = sum(pos_in$median_outscore_pos)
indegree_neg = sum(neg_in$median_outscore_neg)

weighted_outdegree = outdegree_pos - outdegree_neg
weighted_indegree = indegree_pos - indegree_neg

ar_pos = outdegree_pos/indegree_pos
ar_neg = outdegree_neg/indegree_neg

ic_pos = outdegree_pos * indegree_pos
ic_neg = outdegree_neg * indegree_neg

rm(pos_out, neg_out, outdegree_pos, outdegree_neg, pos_in, neg_in,
   indegree_pos, indegree_neg, weighted_outdegree, weighted_indegree)

forplot_SDG15 = data.frame(SDG = "SDG 15",
                           AR_pos = ar_pos, AR_neg = ar_neg,
                           IC_pos = ic_pos, IC_neg = ic_neg)
```

```{r making plot (AR IC SDG 15) Fig 3b}
onlySDG15 = ggplot() +
  #positive AR/IC
  geom_point(data = forplot_SDG15, aes(x = AR_pos, y = IC_pos), color = "#4393c3", shape = 16, size = 2.5) +
  geom_text_repel(data = forplot_SDG15, aes(x = AR_pos, y = IC_pos, label = SDG),
            color = "#4393c3", size = 2.4) +
  
  #negative AR/IC
  geom_point(data = forplot_SDG15, aes(x = AR_neg, y = IC_neg), color = "#d6604d", shape = 17, size = 2.5) +
  geom_text_repel(data = forplot_SDG15, aes(x = AR_neg, y = IC_neg, label = SDG),
            color = "#d6604d", size = 2.4) +
  
  geom_vline(xintercept = 1) +
  scale_x_continuous(limits = c(0.5, 1.7), trans = "log10",
                     ) + labs(x = "Activity Ratio", y = "Interconnectedness") + 
  annotate(geom = "text", x = 0.75, y = 1500, label = "Buffer", 
           fontface = 'italic', size = 3.5) +
  annotate(geom = "text", x = 1.5, y = 1500, label = "Multiplier", 
           fontface = 'italic', size = 3.5) +
  
  coord_cartesian(ylim = c(0, 3200), clip = "off") +
  
  labs(title = "(b)") +
  
  theme(axis.title = element_text(size = 10),
        axis.text = element_text(size = 7),
        panel.background = element_rect(fill = "#d8d8d8"),
        panel.grid.major = element_line(size = 0.45, linetype = "solid", colour = "#F0F0F0"),
        panel.grid.minor = element_line(size = 0.45, linetype = "solid", colour = "#F0F0F0"),
        plot.margin = unit(c(0.8,0,0.8,0), "cm"))
  

onlySDG15

#exporting this
png(filename = "Figure3b.png",
    width = 1000,
    height = 750,
    res = 300)
onlySDG15
dev.off()

#note: We manually combine Fig 3a and 3b outside of R.
rm(bm_all, forplot, forplot_SDG15, onlySDG15, maindat, sdgstat_all,
   ar_neg, ar_pos, ic_neg, ic_pos)
```

# Fig. 4
```{r requirements2}
library(corrplot)
library("Hmisc")
#note: use the Hmisc library only after the pervious chunks since using it after will lead to masking of some functions which will require adjustments in the code
```

```{r reading data - Fig 4.}
maindat = read_excel("Alldata.xlsx", sheet = "method2")
options(scipen = 999, digits = 2)

#sign change to indicators whose increment is undesirable
tonegative = function(x){x = -1*x}
maindat[, c("undernourishment", "food_insecurity", "death_chronic", "suicide", "consumption_gdp", "consumption_all", "consumption_cap", "death_missing")] = lapply(maindat[, c("undernourishment", "food_insecurity", "death_chronic", "suicide", "consumption_gdp", "consumption_all", "consumption_cap", "death_missing")], tonegative)
```

```{r calculating correlations}
corrtable =  rcorr(data.matrix(maindat[,2:22]), type = "spearman")
corrtable_pval = as.data.frame(corrtable[["P"]])
corrtable_r = as.data.frame(corrtable[["r"]])

corrtable_r[is.na(corrtable_r)] = 0

corrtable_pval[is.na(corrtable_pval)] = 0

#Extracting only those correlations that falls between -1 to -0.6 and 0.6 to 1 whose pvalue > 0.05
for(j in 1:nrow(corrtable_r)) {
  for(i in 1:ncol(corrtable_r)){
    if(corrtable_pval[j,i] > 0.05) {
      corrtable_r[j,i] = 0
    }
    if(corrtable_r[j,i] > -0.6 && corrtable_r[j,i] < 0.6) {
      corrtable_r[j,i] = 0
    }
  }
}

rownames(corrtable_r) = colnames(corrtable_r)
```
```{r adjusting labels for figure (Fig. 4)}
rownames(corrtable_r) = c("Forest cover % of total Area (15.1.1b)",
                          "Freshwater KBAs covered by protected areas (15.1.2a)",
                          "Terrestrial KBAs covered by protected areas (15.1.2b)",
                          "Red List Index (15.5.1)",
                          "Prevalence of undernourishment (2.1.1)",
                          "Prevalence of food insecurity (2.1.2)",
                          "Mortality rate due to chronic diseases (3.4.1)",
                          "Suicide mortality rate (3.4.2)",
                          "Universal health coverage (3.8.1)",
                          "Women seats in parliament (5.5.1)",
                          "Access to safely managed drinking water (6.1.1)",
                          "Access to electricity (7.1.1)",
                          "Access to clean energy (7.1.2)",
                          "Share of renewable energy (7.2.1)",
                          "Growth rate of GDP per capita (8.1.1)",
                          "Manufacturing value added (9.2.1)",
                          "Domestic material consumption per GDP (12.2.2a)",
                          "Domestic material consumption (12.2.2b)",
                          "Domestic material consumption per capita (12.2.2c)",
                          "Persons affected by disasters (13.1.1)",
                          "Local governments adapting DRR (13.1.3)"
                          )

colnames(corrtable_r) = c("15.1.1b", "15.1.2a", "15.1.2b",
                          "15.5.1", "2.1.1", "2.1.2",
                          "3.4.1", "3.4.2", "3.8.1",
                          "5.5.1", "6.1.1", "7.1.1",
                          "7.1.2", "7.2.1", "8.1.1", 
                          "9.2.1", "12.2.2a", "12.2.2b",
                          "12.2.2c", "13.1.1", "13.1.3")
```

  Making the correlation plot
```{r making and saving plot (Fig. 4)}
#making the corrplot

png(filename = "Figure4.png",
    height = 1200,
    width = 1600,
    res = 120)

corrplot(as.matrix(corrtable_r),
         diag = FALSE, type = "upper", tl.cex = 1.1, tl.col = c(rep("#006d2c", 4), rep("black", 17)))

rm(corrtable, corrtable_pval, corrtable_r, maindat,i, j, tonegative)
```

  
# Fig. 5
```{r requirements3}
library(ggpattern)
```

Reading data
```{r reading data}
maindat = read_xlsx('Alldata.xlsx', sheet = "method3")
maindat$Description = factor(maindat$Description, levels  = c("Peace and justice (SDG 16)",
                                                "Sustainable cities/communities (SDG 11)",
                                                "Reduced inequalities (SDG 10)",
                                                "Industry and infrastructure (SDG 9)",
                                                "Economic growth (SDG 8)",
                                                "Affordable and clean energy (SDG 7)",
                                                "Clean water and sanitation (SDG 6)",
                                                "Gender equality (SDG 5)",
                                                "Quality education (SDG 4)",
                                                "Good health and well-being (SDG 3)",
                                                "Zero hunger (SDG 2)",
                                                "No poverty (SDG 1)"))
                                                
                                                
```

```{r making and saving plot - Fig 5}
maindat$Interaction = factor(maindat$Interaction, levels = c("Co-benefit", "Trade-off"))
maindat$Type = factor(maindat$Type, levels = c("Outgoing", "Incoming"))

maindat$fill_color = ifelse(maindat$Interaction == "Co-benefit", "#588DB8", "#9E2A2B")

fullplot = ggplot(data = maindat) +
  geom_bar(aes(x = Description, y = Count), position = "stack", stat = "identity") +
  
   geom_bar_pattern(aes(x = Description, y = Count, pattern = Type),
                    stat = "identity", color = c(rep("#588DB8", 24), rep("#9E2A2B", 24)), 
                    fill = "white", pattern_color = c(rep("#588DB8", 24), rep("#9E2A2B", 24))) +
  
  facet_grid(cols = vars(Interaction))+
  
   coord_flip() +
  
   theme(axis.text.x = element_text(hjust = 1),
    legend.position = "bottom",
    axis.title.x = element_text(size = 8),
    axis.title.y = element_text(size = 8),
    axis.text = element_text(size = 7.5),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(size = 0.15, linetype = "solid", colour = "#F0F0F0"),
    panel.grid.minor = element_line(size = 0.15, linetype = "solid", colour = "#F0F0F0"))
  
fullplot
```

  Saving this plot
```{r}
#Saving the plot
png(filename = "Figure5.png",
    width = 800,
    height = 800,
    res = 120)

fullplot

dev.off()

rm(fullplot, maindat)
```
  
# Fig. 6
For figure 6, we use a different excel file
```{r adding and cleaning data}
#1. Expert Online Survey
alldata1 = read_excel("ForSynthesisTable.xlsx", sheet = "OnlineSurvey")
maindata1 = alldata1 %>% select(Goal, Score, n)
colnames(maindata1) = c("SDG", "Interaction", "Count")
maindata1 = maindata1 %>% mutate(Interaction = fct_case_when(
  Interaction == "Positives" ~ "Co-benefit",
  Interaction == "Negatives" ~ "Trade-off",
  Interaction == "Neutral" ~ "Neutral"
))
maindata1 = maindata1 %>% group_by(Interaction)%>%
  dplyr::summarize(n = sum(Count))
maindata1 = maindata1 %>% mutate(Method = c(rep("SDG interaction scores")))

#2. Correlation
alldata2 = read_excel("ForSynthesisTable.xlsx", sheet = "Correlation")
maindata2 = pivot_longer(alldata2, starts_with("SDG"), 
                         names_to = "SDG")
colnames(maindata2) = c("Interaction", "SDG", "Count")
maindata2 = maindata2 %>% group_by(Interaction) %>%
  dplyr::summarize(n = sum(Count))
maindata2 = maindata2 %>% mutate(Interaction = fct_case_when(
  Interaction == "Positive" ~ "Co-benefit",
  Interaction == "Negative" ~ "Trade-off",
  Interaction == "Neutral" ~ "Neutral"
)) %>% mutate(Method = c(rep("Correlation analysis")))


#3. Key Informant Interviews
alldata3 = read_excel("ForSynthesisTable.xlsx", sheet = "KII")
maindata3 = alldata3 %>% select(Goal,Type, Count)  
colnames(maindata3) = c("SDG", "Interaction", "Count")
maindata3 = maindata3 %>% group_by(Interaction) %>%
  dplyr::summarize(n = sum(Count))
maindata3 = maindata3 %>% mutate(Interaction = fct_case_when(
  Interaction == "Synergies" ~ "Co-benefit",
  Interaction == "Tradeoff" ~ "Trade-off"
)) %>% mutate(Method = c(rep("Expert elicitation")))
```

Combining these into one table:
```{r combined table}
maindata = rbind(maindata1, maindata2, maindata3)
maindata$Method = factor(maindata$Method, levels = c("SDG interaction scores", "Correlation analysis", "Expert elicitation"))
maindata$Interaction = factor(maindata$Interaction,
                              levels = c("Co-benefit", "Neutral", "Trade-off"))

maindata = maindata %>% group_by(Method) %>%
 mutate(percent = round(n/sum(n),2))
```

```{r making the plot}
comparisonplot = ggplot(data = maindata, aes(x = Method, y = percent, fill = Interaction)) + 
  geom_bar(stat = "identity", position = "fill") +
 geom_text(aes(x = Method, y = percent, label= paste0(percent*100, " %")),
           position = position_fill(vjust = 0.5), colour = "black") +
  scale_fill_manual(values = c("#588DB8", "#CFCFCF", "#9E2A2B")) +
  scale_y_continuous(labels = function (y) y*100) +
  
  theme(
    legend.text = element_text(size = 12),
    legend.title= element_blank(),
    legend.position = "bottom",
    axis.text.x = element_text(size = 12),
    axis.title = element_blank(),
    axis.text.y = element_blank(),
  # axis.ticks = element_line(colour = "grey70", linewidth = 0.1),
   panel.grid.major.y = element_line(colour = "#e5e5e4", linewidth = 0.1),
    panel.grid.minor.y = element_line(colour = "#e5e5e4", linewidth = 0.1),
   panel.background = element_blank()
    ) 

comparisonplot

#saving to file
png(filename = "Figure6.png",
    width = 800,
    height = 800,
    res = 120)
comparisonplot
dev.off()


rm(alldata1, alldata2, alldata3, comparisonplot, maindata1,
   maindata2, maindata3, maindata)
```

# Fig. 7
```{r adding and cleaning the data}
syndat <- read_excel("Alldata.xlsx", sheet = "allmethods")

syndat$SDG = factor(syndat$SDG, levels = c("SDG 17", "SDG 16", paste("SDG", seq(13, 1, -1))))
syndat = syndat %>% mutate(Approach = fct_case_when(
  Approach == "Interaction Scores" ~ "SDG interaction scores",
  Approach == "Temporal Analysis" ~ "Correlation analysis",
  Approach == "Interview" ~ "Expert elicitation"
))

syndat$Interaction = factor(syndat$Interaction, levels = c("Co-benefit", "Neutral", "Trade-off"))

syndat = syndat %>% 
  mutate(image = fct_case_when(
  SDG == "SDG 1" ~ "Goal-01.png",
  SDG == "SDG 2" ~ "Goal-02.png",
  SDG == "SDG 3" ~ "Goal-03.png",
  SDG == "SDG 4" ~ "Goal-04.png",
  SDG == "SDG 5" ~ "Goal-05.png",
  SDG == "SDG 6" ~ "Goal-06.png",
  SDG == "SDG 7" ~ "Goal-07.png",
  SDG == "SDG 8" ~ "Goal-08.png",
  SDG == "SDG 9" ~ "Goal-09.png",
  SDG == "SDG 10" ~ "Goal-10.png",
  SDG == "SDG 11" ~ "Goal-11.png",
  SDG == "SDG 12" ~ "Goal-12.png",
  SDG == "SDG 13" ~ "Goal-13.png",
  SDG == "SDG 16" ~ "Goal-16.png",
  SDG == "SDG 17" ~ "Goal-17.png"
))

```
  Making the figure::
```{r Fig 7 plot}
figure = ggplot(data = syndat, aes(x = SDG, y = pc, fill = Interaction)) +
    scale_fill_manual(values = c("#588DB8", "#CFCFCF" ,"#9E2A2B")) +
  
  geom_col(position = "stack") +
  
  geom_text(aes(label = ifelse(Interaction == "Neutral", "",  
                  ifelse(pc > 0, paste0(pc*100, "%"), ""))),
           position = position_fill(vjust = 0.5), colour = "black", size = 6) +
  
  facet_grid(cols = vars(Approach),
             ) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  #geom_image(data = syndat, aes(x = SDG, y = -0.1, image = image), size = 0.1) +
 # coord_cartesian(ylim = c(0, 1), clip = "off") +

  
     theme(
        legend.text = element_text(size = 20),
        legend.title = element_text(size = 25),
        legend.position = "bottom",
        axis.text.x = element_text(size = 18),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 20), #to increase size of facets
        panel.spacing = unit(1, "lines")) +
  coord_flip()

figure

#saving it to file::
png(filename = "Figure7.png",
    width = 1600,
    height = 1700,
    res = 120)

figure

dev.off()

#note: the SDGs are ascending (starts with SDG 1 in the top until SDG 17 in the bottom)
#the logo for each SDGs were added manually
```
